Project Light

### 2015-09-02 paper/paper.tex
formulate the other paragraphs from the introduction

- this paper proposes a way to transmit initial keying material for sec layers from smart phone via light
- should be an alternative for private users
- basic setup:
	- smart phone application allows to input keying material and parameters
	- on first start, uninitialized mote load keying initialization program
	- smart phone encodes keying material and transmits it as flickering light
	- mote reads brightness values and reconstructs keying material
	- if transmission was successful, keying material is permanently stored on mote
	- on later start-ups, the mote don't reinitializes again, but uses stored keying material
- why:
	- light sensors are smaller than plugs
	- physics of light is good understood by non-technical people
	- multiple devices could be programmed concurrently

- we implemented prototype using an android smart phone and a Contiki mote
- Contiki is an open source operating system for IoT
- we've implemented two versions of an application for the smart phone
- we've tested various techniques to make transmission error-prone
- we've tested, how fast we could get transmitting with high chance of correctness

>>>>

This paper proposes an alternative way to transmit initial keying material via light.
It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.

In a nutshell, the user utilizes a smart phone application to enter, encode and emit keying material using the flash light of the phone.
The mote receives the message via a light sensor and reconstructs the keys.
After successful initialization and verification, the mote saves the keying material permanently.
On subsequent reboots, it is read from memory and immediately usable without any further action required.

There are several advantages of this method.
Light sensors are smaller and less misusable than jacks.
The physics of light is well understood by non-technical people, in contrast to radio waves.
Thus, leaking of the wireless sent information is less likely.
Moreover, multiple devices could be programmed concurrently by just placing them next to each other.

We implemented prototype for an Android smart phone and a Contiki\footnote{http://www.contiki-os.org/} mote.
Contiki is an open source, state-of-the-art operating system for IoT devices.
For the Android phone, we implemented two versions of a light emitting application.
We have tested some techniques to make the transmission error-prone.
Besides, we examined how fast the whole transmission could become while maintaining a high chance of correctness.
